Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-03 docs/msr.tex
added experiment section

\subsection{Data Provenance and Processing}
\label{sec:data}

@@

Our experiment involved three entities: a Rabbit{\sc mq}
server,\footnote{\url{http://www.rabbitmq.com/}} a Python pool of worker
processes and a mongo{\sc db}.\footnote{\url{http://www.mongodb.org/}}

>>>>

Our experiment goal was to collect the metric results of the findbugs tool.
The process involved three entities: a number of \textit{workers}, a \textit{task queue} mechanism,
a \textit{data repository}, and the \textit{code repository}, which in our case it was the public Maven 
repository\footnote{\url{http://mvnrepository.com}}.

\begin{table}
\centering
\caption{Experiment software and versions}
\label{tbl:soft-version}
\begin{tabular}{r r r}
\hline
 & Software Package & version\\
 \hline
worker & Custom Python Script & 2.7\\
task queue & RabbitMQ\footnote{\url{http://www.rabbitmq.com/}} & \\
data repository & MongoDB\footnote{\url{http://www.mongodb.org/}} & \\
code repository & Maven Repository & \\
\hline
\end{tabular}
\end{table}

First, we scanned the Maven repository for appropriate jars. We discuss the the jar selection process in the next 
section. With this list we created a series of processing tasks and added them to the \textit{task queue}. Then we
executed 25 (unix-based) workers that checked out tasks from the queue, processed the data and stored the results to the \textit{data repository}.

A typical processing cycle included the following steps:

\begin{enumerate}
	\item The worker spawns,
	\item then it requests a task from the queue,
	\begin{enumerate}
		\item the tasks contains the {\sc jar}, which is typically a project version and it is downloaded,
		\item and the {\sc jar} metadata and statistics are also analysed and stored,
		\item then findbugs is executed,
		\item and the results are stored in the data repository,
		\item the queue is also notified that this task is completed,
	\end{enumerate}
	\item then the next task is requested from the queue.
\end{enumerate}

This process was executed for all the available {\sc jar}s in the \textit{task queue}. The experiment was executed 5 times in order to iron out various bugs in our scripts and validate the results.

\subsection{Data Provenance}
\label{sec:data}

@@
